onsetsync demo

### 2022-11-10 README.Rmd
Added links to Rmd and ipynb

For more examples, see [Get started](docs/articles/onsetsync.html).

>>>>

## More information

For more examples, see [Get started](https://tuomaseerola.github.io/onsetsync/articles/onsetsync.html).

- [Tutorial in Rmarkdown](https://github.com/tuomaseerola/onsetsync/blob/master/onsetsync.Rmd) which requires you to run the code in RStudio.

- [Tutorial as Jupyter notebook](https://github.com/tuomaseerola/onsetsync/blob/master/onsetsync.ipynb) which allows you to run the code in Colab (in your browser).
